\chapter*{Acknowledgments}

First and foremost, I would like to express my sincere gratitude to my advisor Prof. Kento Aida for the continuous support of my Ph.D. study, for his patience, motivation, enthusiasm, and immense knowledge.
His guidance helped me in all the time of research and writing of this thesis.
I could not have imagined having a better advisor and mentor for my Ph.D. study.

Besides my advisor, I would like to sincerely thank the rest of my thesis committee: Prof. Atsuko Takefusa, Prof. Michihiro Koibuchi, Prof. Takashi Kurimoto, and Prof. Shigetoshi Yokoyama, for their patience, encouragement, insightful comments, and hard questions.

I am deeply grateful to my former and current fellow lab members at National Institute of Informatics, Kai Liu, Takeshi Nishimura, Zhang Yongzhe, Dr. Jingtao Sun, Dr. Tomoya Tanjo, and Dr. Kazushige Saga for the stimulating discussions.
In the course of the study, I sometimes got stressed and lost enthusiasm in the research activity itself.
In such occasions, I was often \replaced[id=5th]{inspired}{impressed} by their sincere attitude toward knowledge and encouraged by some advises they gave me through the chat.
\added[id=5th]{
I also thank the administrative staff of the Aida lab, Ms. Morimoto, for her support and patience when I was not able to respond to her e-mail quickly.
}



Also, I thank my colleagues at Cluster Computing Inc., Koichirou Moria, and Tomoko Kakizawa, for their help in my daily responsibilities at my job.
Without their help, I could not have even managed to spare the time to conduct research activities in the first place.



I would also like to extend thanks to former colleagues at Fujitsu laboratories Limited, where I was a member of from 1993 until 2002.
During that time, I acquired the necessary skills to conduct research and development.
Especially among them are my ex-boss Dr. Hiroshi Arimoto at Fujitsu Labs., and late Prof. Hideaki Fujitani at The University of Tokyo.
Dr. Hiroshi Arimoto, who helped me to enroll in the doctoral program, has also inspired me with his scientific way of thinking for a long time.
Late Prof. Hideaki Fujitani helped me join Fujitsu Labs., and had been always a mentor while I was at that company.
Professors Fujitani's passing in January in 2019 saddened me deeply.



I am also grateful to Professor Emeritus Dr. Fabian Pease, former Professor Dr. Dan Meiseburger and former colleague Dr. Liqun Han at Stanford University for allowing me to work with them back in 1999-2000.
Although the research topic back then is not directly related to this thesis, inspirations I got from them were so valuable that I could go back to academia this time.



Last but not least, I would like to thank my family members: My parents Akiko Takahashi and Nobuo Takahashi, for always supporting me throughout my life.
My son Yuki and daughter Hanae, have given me every reason in my life.
Above all, the exceptional thanks are due to my wife Junko for always being with me. I owe you everything.


\begin{flushright}
{\em\Large Kimitoshi Takahashi} \par\medskip {\em\large September 2019}
\end{flushright}





